Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
more section 4 edits

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere within
the photometric aperture of the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

We find that four of the presented candidates have FPP $>$90\%;
these we consider to be likely false positives.
On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; we consider these to be statistically validated planets.
Of these, 18 are validated for the first time.
The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.

We emphasize that the majority of these planets were validated based
solely on the transit signal, with no need for follow-up imaging.  This
demonstrates the utility of \texttt{vespa} analysis, which will be
crucial to interpreting future candidates detected by \KT, TESS, and PLATO
and prioritizing follow-up observing efforts.
We show these transit signals as Fig. \ref{fig:transits}.

@@

We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
companion.
From the transit shape, we can rule out the possibility this system is a background eclipsing
binary.
Regardless of which star this object transits, the object is planet-sized.
In Table 3, we assume the planet is orbiting the larger star. 
If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
account for the observed transit depth.

@@

\subsection{Known Background Stars}
The PHARO AO system has a field of view of 25 arcseconds.
Each \KT\ pixel is a square, $3\farcs98$ on a side.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal inside our aperture while evading detection
by PHARO.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

>>>>

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation 
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

We find that four of the presented candidates have FPP $>$90\%;
these we consider to be likely false positives.
On the other hand, we find that 21 candidates
have FPP $<$ 1\%.  
Two of these we find to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

This leaves 15 candidates that we statistically validate as planets, plus three
additional planets that \texttt{vespa} does not validate but have been previously
identified in the literature \citep{Crossfield15, Armstrong15b}.  
So in total, of the 36 candidates, 18 are secure planets, 
14 of which we here validate for the first time.

We emphasize that the majority of these validations rely
solely on the transit photometry and SDSS data, with no need for follow-up imaging.  This
demonstrates the utility of the \texttt{vespa} tool, which will be
crucial to interpreting future candidates detected by \KT, TESS, and PLATO
and prioritizing follow-up observing efforts.
We show the transit signals in Fig. \ref{fig:transits}.

@@

%We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
%companion.
%From the transit shape, we can rule out the possibility this system is a background eclipsing
%binary.
%Regardless of which star this object transits, the object is planet-sized.
%In Table 3, we assume the planet is orbiting the larger star. 
%If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
%account for the observed transit depth.

@@

\subsection{Known Background Stars}
\label{sec:background}
The PHARO AO system has a field of view of 25 arcseconds.
Each \KT\ pixel is a square, $3\farcs98$ on a side.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal inside our aperture while evading detection
by PHARO.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.
